Component response rate variation underlies the stability of complex systems

### 2020-03-20 notebook/SI.Rmd
Insert cascade food web model results into the SI

```{r, echo = FALSE, fig.align = "center"}
sfn <- read.csv(file = "sim_results/sfn/sfn.csv"); # Change when new results are in
use <- c(1:6, 19:21);
kable(sfn[,use]);
```

As in small-world networks, the mean $C$ is shown, along with the mean complexities of $\mathbf{A}$ and $\mathbf{M}$. Like all other networks, $\sigma^{2}_\gamma$ increases the stability of scale-free networks given sufficiently complexity, but the complexity requires seems to be relatively low.

>>>>

```{r, echo = FALSE, fig.align = "center"}
sfn <- read.csv(file = "sim_results/sfn/sfn.csv"); 
use <- c(1:6, 19:21);
kable(sfn[,use]);
```

As in small-world networks, the mean $C$ is shown, along with the mean complexities of $\mathbf{A}$ and $\mathbf{M}$. Like all other networks, $\sigma^{2}_\gamma$ increases the stability of scale-free networks given sufficiently high complexity.

Cascade food webs are saturated, and similar to predator-prey random networks. What distinguishes them from predator-prey networks is that cascade food webs are also defined by intactions in which components are ranked such that if the rank of $i > j$, then $A_{ij} < 0$ and $A_{ji} > 0$. In other words, if interpreting components as ecological species, species can only feed off of a species of lower rank. The table below shows how $\sigma^{2}_\gamma$ affects stability across system sizes in cascade food webs.

```{r, echo = FALSE, fig.align = "center"}
csc <- read.csv(file = "sim_results/ecology/cascade_C_1.csv"); 
use <- c(1:5, 18:19);
kable(csc[,use]);
```

Cascade food webs are more likely to be stable than small-world or scale-free networks at equivalent magnitudes of complexity (note that $C = 1$ for all above rows). A higher number of stable $\mathbf{M}$ than $\mathbf{A}$ was found given $S \geq 27$.

### 2020-03-20 notebook/SI.tex
Insert cascade food web model results into the SI

As in small-world networks, the mean \(C\) is shown, along with the mean
complexities of \(\mathbf{A}\) and \(\mathbf{M}\). Like all other
networks, \(\sigma^{2}_\gamma\) increases the stability of scale-free
networks given sufficiently complexity, but the complexity requires
seems to be relatively low.

@@

\includegraphics{SI_files/figure-latex/unnamed-chunk-29-1.pdf}

@@

{\centering \includegraphics{SI_files/figure-latex/unnamed-chunk-33-1}

@@

\includegraphics{SI_files/figure-latex/unnamed-chunk-35-1.pdf}

@@

\includegraphics{SI_files/figure-latex/unnamed-chunk-40-1.pdf}

@@

>>>>

As in small-world networks, the mean \(C\) is shown, along with the mean
complexities of \(\mathbf{A}\) and \(\mathbf{M}\). Like all other
networks, \(\sigma^{2}_\gamma\) increases the stability of scale-free
networks given sufficiently high complexity.

Cascade food webs are saturated, and similar to predator-prey random
networks. What distinguishes them from predator-prey networks is that
cascade food webs are also defined by intactions in which components are
ranked such that if the rank of \(i > j\), then \(A_{ij} < 0\) and
\(A_{ji} > 0\). In other words, if interpreting components as ecological
species, species can only feed off of a species of lower rank. The table
below shows how \(\sigma^{2}_\gamma\) affects stability across system
sizes in cascade food webs.
S & A\_unstable & A\_stable & M\_unstable & M\_stable & complex\_A &
complex\_M\tabularnewline
2 & 0 & 1000000 & 0 & 1000000 & 0.6378839 & 0.6381485\tabularnewline
3 & 1 & 999999 & 1 & 999999 & 0.7055449 & 0.7525143\tabularnewline
4 & 2 & 999998 & 2 & 999998 & 0.8060500 & 0.8826100\tabularnewline
5 & 17 & 999983 & 17 & 999983 & 0.8974749 & 0.9967594\tabularnewline
6 & 42 & 999958 & 43 & 999957 & 0.9821323 & 1.0999762\tabularnewline
7 & 124 & 999876 & 124 & 999876 & 1.0600906 & 1.1938910\tabularnewline
8 & 303 & 999697 & 309 & 999691 & 1.1329713 & 1.2807302\tabularnewline
9 & 653 & 999347 & 661 & 999339 & 1.2009135 & 1.3616372\tabularnewline
10 & 1401 & 998599 & 1413 & 998587 & 1.2661142 &
1.4387567\tabularnewline
11 & 2534 & 997466 & 2566 & 997434 & 1.3276636 &
1.5113096\tabularnewline
12 & 4514 & 995486 & 4597 & 995403 & 1.3865754 &
1.5804005\tabularnewline
13 & 7570 & 992430 & 7722 & 992278 & 1.4424479 &
1.6462780\tabularnewline
14 & 12223 & 987777 & 12502 & 987498 & 1.4970134 &
1.7102322\tabularnewline
15 & 18433 & 981567 & 18879 & 981121 & 1.5498812 &
1.7719564\tabularnewline
16 & 26973 & 973027 & 27712 & 972288 & 1.6002970 &
1.8310447\tabularnewline
17 & 38272 & 961728 & 39499 & 960501 & 1.6494195 &
1.8884211\tabularnewline
18 & 52397 & 947603 & 54099 & 945901 & 1.6975099 &
1.9443860\tabularnewline
19 & 69986 & 930014 & 72342 & 927658 & 1.7439233 &
1.9987398\tabularnewline
20 & 92851 & 907149 & 95776 & 904224 & 1.7893524 &
2.0514394\tabularnewline
21 & 117487 & 882513 & 121095 & 878905 & 1.8335974 &
2.1030121\tabularnewline
22 & 147852 & 852148 & 151989 & 848011 & 1.8761874 &
2.1527108\tabularnewline
23 & 183501 & 816499 & 187888 & 812112 & 1.9186092 &
2.2019827\tabularnewline
24 & 222592 & 777408 & 226021 & 773979 & 1.9591518 &
2.2491948\tabularnewline
25 & 267691 & 732309 & 269822 & 730178 & 1.9999089 &
2.2963949\tabularnewline
26 & 316090 & 683910 & 316371 & 683629 & 2.0396325 &
2.3427211\tabularnewline
27 & 369830 & 630170 & 366550 & 633450 & 2.0785319 &
2.3879356\tabularnewline
28 & 426407 & 573593 & 419136 & 580864 & 2.1169703 &
2.4324407\tabularnewline
29 & 485068 & 514932 & 473666 & 526334 & 2.1545265 &
2.4759539\tabularnewline
30 & 544300 & 455700 & 527568 & 472432 & 2.1912376 &
2.5187795\tabularnewline
31 & 605803 & 394197 & 584385 & 415615 & 2.2271037 &
2.5603818\tabularnewline
32 & 664689 & 335311 & 638047 & 361953 & 2.2626270 &
2.6016360\tabularnewline
33 & 718848 & 281152 & 689172 & 310828 & 2.2979241 &
2.6424881\tabularnewline
34 & 770790 & 229210 & 737639 & 262361 & 2.3327303 &
2.6828460\tabularnewline
35 & 817531 & 182469 & 783112 & 216888 & 2.3666720 &
2.7221952\tabularnewline
36 & 858750 & 141250 & 823548 & 176452 & 2.3998286 &
2.7608037\tabularnewline
37 & 893017 & 106983 & 859194 & 140806 & 2.4332806 &
2.7994470\tabularnewline
38 & 921268 & 78732 & 890177 & 109823 & 2.4658414 &
2.8372307\tabularnewline
39 & 943551 & 56449 & 915655 & 84345 & 2.4974678 &
2.8741350\tabularnewline
40 & 961088 & 38912 & 936883 & 63117 & 2.5301278 &
2.9116114\tabularnewline
41 & 973664 & 26336 & 953645 & 46355 & 2.5616210 &
2.9481298\tabularnewline
42 & 982829 & 17171 & 967044 & 32956 & 2.5925309 &
2.9841081\tabularnewline
43 & 989464 & 10536 & 977033 & 22967 & 2.6228949 &
3.0191690\tabularnewline
44 & 993622 & 6378 & 984470 & 15530 & 2.6534626 &
3.0548439\tabularnewline
45 & 996221 & 3779 & 989678 & 10322 & 2.6832092 &
3.0890543\tabularnewline
46 & 997963 & 2037 & 993318 & 6682 & 2.7130588 &
3.1236201\tabularnewline
47 & 998818 & 1182 & 995957 & 4043 & 2.7423480 &
3.1575904\tabularnewline
48 & 999422 & 578 & 997446 & 2554 & 2.7714223 & 3.1912463\tabularnewline
49 & 999746 & 254 & 998532 & 1468 & 2.7999596 & 3.2244020\tabularnewline
50 & 999864 & 136 & 999132 & 868 & 2.8285547 & 3.2574510\tabularnewline
51 & 999934 & 66 & 999561 & 439 & 2.8566907 & 3.2900943\tabularnewline
52 & 999970 & 30 & 999761 & 239 & 2.8844703 & 3.3222721\tabularnewline
53 & 999985 & 15 & 999873 & 127 & 2.9122645 & 3.3544290\tabularnewline
54 & 999999 & 1 & 999935 & 65 & 2.9395400 & 3.3859103\tabularnewline
55 & 1000000 & 0 & 999971 & 29 & 2.9665996 & 3.4173273\tabularnewline
56 & 999999 & 1 & 999988 & 12 & 2.9936263 & 3.4486027\tabularnewline
57 & 1000000 & 0 & 999989 & 11 & 3.0199283 & 3.4789408\tabularnewline
58 & 1000000 & 0 & 999998 & 2 & 3.0460952 & 3.5094530\tabularnewline
59 & 1000000 & 0 & 999999 & 1 & 3.0728115 & 3.5401634\tabularnewline
60 & 1000000 & 0 & 1000000 & 0 & 3.0983367 & 3.5698067\tabularnewline

Cascade food webs are more likely to be stable than small-world or
scale-free networks at equivalent magnitudes of complexity (note that
\(C = 1\) for all above rows). A higher number of stable \(\mathbf{M}\)
than \(\mathbf{A}\) was found given \(S \geq 27\).

@@

\includegraphics{SI_files/figure-latex/unnamed-chunk-30-1.pdf}

@@

{\centering \includegraphics{SI_files/figure-latex/unnamed-chunk-34-1}

@@

@@

@@

\includegraphics{SI_files/figure-latex/unnamed-chunk-44-1.pdf}
